Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-01-28 ms.tex
more

Appendix \ref{app:windheat} provides a calculation of wind heating rate from stellar winds, $v_{\rm w}^{\star}$, and the mass loss parameter, $\eta$ (eq.~[\ref{eq:q}]), as a function of age $\tau_{\star}$ of a stellar population which is formed impulsively (Figs.~\ref{fig:vwimp}, \ref{fig:etaImp}).  At very early times after the starburst ($\tau_{\star} \lesssim 10^{7}$), the wind heating rate exceeds 1000 km s$^{-1}$, while at much later times ($\tau_{\star} \sim t_{\rm h}$) stellar wind heating is much lower, $v_{\rm w} \sim 50 $ km s$^{-1}$ (see also \citealt{NaimanSoares-Furtado+:2013a}).  As we describe in $\S$, the net heating rate produced by stellar winds in the case of quasi-continuous star formation, as representative of the average star formation history of low mass galaxies, can also be significant, $v_{\rm w}^{\star} \gtrsim 1000$ km s$^{-1}$.  Thus stellar winds contribute a potentialy important source of energy as well as mass for the CNM.

@@

\subsection{Combined Heating Rate}

@@

For each $\Mbh$ we may check whether the solution for corresponding
$\vwO$ and $\eta$ would be thermally stable, using
equation~\eqref{eq:cooling2} {\bf: AG--double check that this is
  equivalent to what I did.}

The combined heating rate from stellar winds and Compton heating is
insufficient to prevent thermal instability for the high $\Mbh$.  This
is shown in Figure~\ref{fig:cooling2}, which shows the heating over
cooling rate at $\rs$ as a function of $\Mbh$. For $\Mbh\gsim 10^8
\Msun$, the cooling rate will exceed the cooling rate at $\rs$ and
and the gas would be thermally unstable.

@@

Although, in principle the Ia contribution to the heating is
substantial, in practice Ia's occur too infrequently to be a steady
contribution to the heating rate on small scales (e.g. $r_{\rm Ia} >
r_{\rm s}$ as shown in Figure~\ref{fig:rs_rIa}). Thus, SNe Ia heating
by itself would not be able to prevent cooling instability.

@@

% Figure~\ref{fig:vweff} shows an estimate of how the combined heating
% depends on the age of the stellar population $\tage$ and the SMB mass
% $\Mbh$.  For $M_{\bullet} \gtrsim 1.5\times 10^8 (\tau_{\star}/t_{\rm
%   h})^{0.5} \Msun$, SNe Ia occur sufficiently frequently within the
% stagnation radius (i.e., $r_{\rm Ia} > r_{\rm s}$; eq.~[\ref{eq:rIa}])
% to contribute their full heating rate.  $v_{w}^{\rm Ia} \sim
% 250$ km s$^{-1}$.  On the other hand, for lower mass BHs Ia SNe are
% infrequent, in which case main sequence stars ($v_{w}^{\star}
% \simeq 100-150$ km s$^{-1}$) dominate the heating at most times of
% interest.\footnote{Although SN Ia will still occur surrounding low
%   mass SMBHs, if they are infrequent interior to the radius where the
%   accretion rate is being set, then they will not affect the flow near
%   the SMBH at most epochs.}  For very young stellar populations
% ($\tage \lsim 10^7$ years), $\vwO\simeq 1000$ km s$^{-1}$ due to
% contributions from line driven winds from high mass main sequence
% stars.
{\bf AG: We should mention that regime with stellar wind heating only
  is likely to be thermally unstable.}

>>>>

Appendix \ref{app:windheat} provides a calculation of wind heating rate from stellar winds, $v_{\rm w}^{\star}$, and the mass loss parameter, $\eta$ (eq.~[\ref{eq:q}]), as a function of age $\tau_{\star}$ of a stellar population which is formed impulsively (Figs.~\ref{fig:vwimp}, \ref{fig:etaImp}).  At very early times after the starburst ($\tau_{\star} \lesssim 10^{7}$), the wind heating rate exceeds 1000 km s$^{-1}$, while at much later times ($\tau_{\star} \sim t_{\rm h}$) stellar wind heating dominated by main sequence winds is much lower, $v_{\rm w} \sim 50-100 $ km s$^{-1}$ (see also \citealt{NaimanSoares-Furtado+:2013a}).  As we describe in $\S$, the net heating rate produced by stellar winds in the case of quasi-continuous star formation, as representative of the average star formation history of low mass galaxies, can also be significant, $v_{\rm w}^{\star} \gtrsim 1000$ km s$^{-1}$.  Thus stellar winds contribute a potentialy important source of energy as well as mass for the CNM.

@@

\subsection{Combined Heating Rate for Representative Star Formation History}

@@

Figure~\ref{fig:cooling2} shows the ratio of heating to radiative cooling at the stagnation radius (eq.~[\ref{eq:cooling2}]) as a function of SMBH mass, using our total heating rate from Figure \ref{fig:vWsources}.  The combined heating rate from stellar winds and Compton heating is insufficient to prevent thermal instability for the high $\Mbh$.  However, if Ia supernovae are included in the schematic way described above, the flow again becomes thermally stable for $\Mbh \gtrsim XXXX$.

%Although, in principle the Ia contribution to the heating is
%substantial, in practice Ia's occur too infrequently to be a steady
%contribution to the heating rate on small scales (e.g. $r_{\rm Ia} >
%r_{\rm s}$ as shown in Figure~\ref{fig:rs_rIa}). Thus, SNe Ia heating
%by itself would not be able to prevent cooling instability.

@@

@@

% Figure~\ref{fig:vweff} shows an estimate of how the combined heating
% depends on the age of the stellar population $\tage$ and the SMB mass
% $\Mbh$.  For $M_{\bullet} \gtrsim 1.5\times 10^8 (\tau_{\star}/t_{\rm
%   h})^{0.5} \Msun$, SNe Ia occur sufficiently frequently within the
% stagnation radius (i.e., $r_{\rm Ia} > r_{\rm s}$; eq.~[\ref{eq:rIa}])
% to contribute their full heating rate.  $v_{w}^{\rm Ia} \sim
% 250$ km s$^{-1}$.  On the other hand, for lower mass BHs Ia SNe are
% infrequent, in which case main sequence stars ($v_{w}^{\star}
% \simeq 100-150$ km s$^{-1}$) dominate the heating at most times of
% interest.\footnote{Although SN Ia will still occur surrounding low
%   mass SMBHs, if they are infrequent interior to the radius where the
%   accretion rate is being set, then they will not affect the flow near
%   the SMBH at most epochs.}  For very young stellar populations
% ($\tage \lsim 10^7$ years), $\vwO\simeq 1000$ km s$^{-1}$ due to
% contributions from line driven winds from high mass main sequence
% stars.
